---
title: "Course Project: US Automotive Fuel Consumption Analyser"
author: "Lee bamber"
date: "26/03/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction 

The Automotive Fuel Consumption Analyser is a Shiny application that will allow the user to interactively analyse the fuel consumption (i.e miles per gallon=mpg) of US automobiles. 

The analysis will include data visualisation, model generation and analysis and prediction. 

The data used for this application is mtcars, which is part of ggplot2 package. 

Use PageUp and PageDown keys to traverse this presentation

## Application Overview- Selection Criteria

There are two selection criteria available in the sidebar.

- **Select box** - The user will be able to select **variable** (e.g number of cylinders,weight) to analyse.

- **Slider** - The user will be able to select a **value** for the variable (e.g 4 cyliners) in order to predict the fuel consumption of an automotive model with that variable value

## Application Overview- Tabular Output

- **First tab (Visualisation)** -  Once a variable is selected, then the first tab will present a visualisation of the relationship between the selected variable (on the x axis ) and mpg (on the y axis). 

- **Second tab (Model Summary)** - A model summary of the linear relationship between the selected variable and mpg will be displayed. This will display the precise mathematical model ( intercept and gradient ) and the metrics that define how well the model fits the data. 

- **Third tab (Prediction)** - Having selected a variable and therefore a model, the user can then select a value of the variable to prdict the fuel consumption (mpg). For example, if Cylenders=cyl is selected as a variable, the user can then see what the fuel consumption of a 6 cylinder car would be. 

## The mtcars Dataset

The analysis will be based upon the mtcars data set, which includes data on 32 US automobile models. The dataset is included in the ggplot2 package.

```{r}
library(ggplot2)
head(mtcars)
```

https://leebamber.shinyapps.io/wk4final/

Click the link below for compiled project files on gitub repo.

https://github.com/lmbamber/DevelopingDataProductsWK4


